\thetitle

### 2017-12-14 TeX/manuscript.tex
began section 2.3

	\node [bordered,red] (vm1) at (0,6.5) {Age of Sibling 1};
	\node [bordered,red] (vm5) at (3,6.5) {Age of Sibling 2};
	\node [bordered,red] (v1) at (0,7.5) {15};
	\node [bordered,red] (v5) at (3,7.5) {20};

@@

>>>>

	\node [bordered,red] (vm1) at (0,6.5) {Age of person 1};
	\node [bordered,red] (vm5) at (3,6.5) {Age of person 2};
	\node [bordered,red] (v1) at (0,7.5) {15};
	\node [bordered,red] (v5) at (3,7.5) {20};

@@

\subsection{An alternative solution}

	In the previous subsection, we attempted to solve the problem of combining logical and numerical symols by converting $True$ into $1$ and $False$ into $2$. In doing this, we noticed that the multiplication operator could be used with a logical symbol to either propogate or to destroy a numerical signal. On the other hand, we were not able to put the addition, subtraction, and division operators to meaningful use, as we were with multiplication. From these results, it should be clear that an alternative solution is necessary. To discover this solution, we will examine a few situations where the two brands of computation are necessary, and formulate how the two can be combined into one family of computations.

(a tree which models a situation where logical and numerical information need to be combined via some operator)

	It is unclear as to how the two should be combined such that the meaning behind each value is retained. In the above situation... (describe how one would combine the two in the above situation to yield the correct output).
